\Recipe{placeholder}{
    Crepes
}{
    \href{https://www.foodnetwork.com/recipes/alton-brown/crepes-recipe-1911037}{Alton Brown}
}{
    \Ingredients{
        \item 2 large eggs
        \item \threefourths \cup milk
        \item \half \cup water
        \item 1 \cup flour
        \item 3 \tablespoons melted butter
        \item Butter, for coating the pan
    }
}{
    \Directions{
        \item In a blender, combine all of the ingredients and pulse for 10 seconds.
            Place the crepe batter in the refrigerator for 1 hour.
            This allows the bubbles to subside so the crepes will be less likely to tear during cooking.
            The batter will keep for up to 48 hours.
        \item Heat a small non-stick pan.
            Add butter to coat.
            Pour 1 \ounce of batter into the center of the pan and swirl to spread evenly.
            Cook for 30 seconds and flip. Cook for another 10 seconds and remove to the cutting board.
            Lay them out flat so they can cool.
            Continue until all batter is gone.
            After they have cooled you can stack them and store in sealable plastic bags in the refrigerator for several days or in the freezer for up to two months.
            When using frozen crepes, thaw on a rack before gently peeling apart.
        \item Savory Variation: Add \fourth \teaspoon salt and \fourth \cup chopped fresh herbs, spinach or sun-dried tomatoes to the egg mixture.
        \item Sweet Variation: Add 2 \half \tablespoons sugar, 1 \teaspoon vanilla extract and 2 \tablespoons of your favorite liqueur to the egg mixture.
    }
}
