\Recipe{
    Earl Grey Crepe Cake
}{
    \href{https://www.socialteahouse.com/blogs/news/how-to-make-lady-ms-earl-grey-crepe-cake}{Social Teahouse}
}{
    \NamedIngredients{Pastry Cream}{
        \item 1 \quarter \cup milk
        \item 3 earl grey teabags
        \item 1 egg
        \item 1 \tablespoon flour
        \item 1 \tablespoon sugar
        \item 1 \tablespoon cornstarch
        \item 1 \teaspoon vanilla extract
    }
    \NamedIngredients{Whipped Cream}{
        \item 2 \cups heavy whipping cream
        \item 2 \tablespoons sugar
        \item 1 early grey teabag
    }
    \NamedIngredients{Crepes}{
        \item 2 \half \cups milk
        \item 5 \tablespoons melted butter
        \item 5 eggs
        \item 1 \quarter \cups all-purpose flour
        \item 3 \tablespoons granulated sugar
        \item 1 pinch of salt
    }
}{
    \Directions{
        \item For the pastry filling, bring the milk to a near boil over medium heat. Once
            simmering, lower the heat and steep the 3 teabags in the milk for about 5 minutes. 
            Meanwhile, whisk together the egg, flour, sugar, and cornstarch in a bowl
            until smooth.
        \item Remove the milk from heat and gradually stir into the egg mixture.
            Return all the ingredients to the stove and keep stirring until thick.
        \item Remove from heat and add vanilla extract.
            Refrigerate until firm.
        \item Whip the cream with a hand mixer.
            Add in the sugar and tea leaves in the earl grey teabag. 
            Slowly fold the earl grey pastry cream into the whipped cream until smooth.
            Refrigerate the filling.
        \item For the crepe batter, heat the 2 \half cups milk until steaming. Remove from heat and let
            cool slightly. 
            In a separate bowl, mix together the 5 eggs, 1 \quarter \cup flour, sugar, butter, and salt.
            Slowly add in the warm milk and mix until smooth.
        \item To make the crepes, pour about \quarter \cup crepe batter in the pan and swirl until
            the surface is covered. 
            Flip after about a minute, or once the edges start crisping up.
            Repeat until you have a stack of 20 crepes.
        \item To assemble the cake, lay down a crepe and evenly spread dollop of the earl grey cream
            filling over the crepe. Lay down another crepe on top. Keep going until the cake is complete.
        \item Once your cake is assembled, cut the tip off a corner of a Ziploc bag and fill with
            leftover cream to pipe whatever decoration you’d like on top, or simply finish with a
            dusting of powdered sugar.
    }
}

