\Recipe{placeholder}{
    Jambalaya
}{
    \href{https://www.tabasco.com/recipe/shrimp-and-sausage-jambalaya/}{Tabasco}
}{
    \Ingredients{
        \item 2 \tablespoons vegetable oil
        \item \half pound andouille or other smoked sausage, cut into \half-inch slices
        \item \half \cup sliced celery
        \item 1 small onion, chopped
        \item 1 small red or green bell pepper, chopped
        \item 1 clove garlic, minced
        \item 1 \threefourths \cups chicken broth
        \item 1 \cup diced fresh or canned tomatoes
        \item 1 bay leaf
        \item 1 \teaspoon TABASCO® brand Original Red Sauce
        \item \fourth \teaspoon dried oregano leaves
        \item \fourth \teaspoon dried thyme leaves
        \item \eighth \teaspoon ground allspice
        \item \threefourths \cup uncooked rice
        \item \half pound shrimp, peeled, deveined and cut in half lengthwise
    }
}{
    \Directions{
        \item Heat oil in a large heavy saucepan or Dutch oven over medium-high heat.
            Add sausage, celery, onion, bell pepper, and garlic.
            Cook 5 minutes or until vegetables are tender, stirring frequently.
        \item Stir in broth, tomatoes, bay leaf, TABASCO Sauce, oregano, thyme, and allspice.
            Bring to a boil, reduce heat, and simmer uncovered for 10 minutes, stirring occasionally.
        \item Stir in rice; cover and simmer 15 minutes.
        \item Add shrimp; cover and simmer 5 minutes longer or until rice is tender and shrimp turn pink.
        \item Let stand, covered, 10 minutes.
            Remove bay leaf before serving.
    }
}
