\Recipe{placeholder}{
    Matcha Crepe Cake
}{
    \href{https://www.youtube.com/watch?v=vfUu0eedUYI}{Just One Cookbook}
}{
    \NamedIngredients{Crepes}{
        \item 1 \threefourths cup whole milk
        \item 3 \tablespoon sugar
        \item 3 eggs
        \item 1 \half \tablespoons melted butter
        \item 1 \cup flour
        \item 3 \tablespoons matcha powder
        \item \half \teaspoon baking powder
    }
    \NamedIngredients{Whipped Cream}{
        \item 1 \cup heavy whipping cream
        \item 3 \tablespoons sugar
    }
}{
    \Directions{
        \item For the crepe batter, heat the milk and sugar until steaming.
            Remove from heat and let cool slightly. 
            In a separate bowl, mix together the eggs, flour, butter, salt, and matcha powder.
            Slowly add in the warm milk and mix until smooth.
        \item To make the crepes, pour about \quarter \cup crepe batter in the pan and swirl until
            the surface is covered. 
            Flip after about a minute, or once the edges start crisping up.
            You want to make one large crepe (10--12 inches) and about 12 small crepes (8 inches).
        \item Whip the cream with a hand mixer.
            Add in the sugar.
            Refrigerate the filling.
        \item To prepare the surface, lay down two strips of parchment paper perpendicular to one another.
            You will assemble the cake upside-down, and use these strips to lift it.
        \item To assemble the cake, lay down the large crepe and evenly spread a dollop of the whipped cream
            filling over the crepe.
            Lay down a small crepe on top. Keep going until the cake is complete.
        \item Once your cake is assembled, lift into a bowl lined with cling film, and wrap up tightly.
            The bowl and wrapping will mold the cake into a beautiful, round shape.
            Refrigerate for at least two hours (preferably overnight) before inverting and serving.
            Top with a light dusting of matcha powder.
    }
}

