\recipe{
    Saag Paneer
}{
    \href{https://www.foodnetwork.com/recipes/aarti-sequeira/saag-paneer-spinach-with-indian-cheese-recipe-1927603}{Aarti Sequeira}
}{
    \Ingredients{
        \item 1 \teaspoon turmeric
        \item \half \teaspoon cayenne
        \item Kosher salt
        \item 3 \tablespoons plus 1 \half \tablespoons vegetable oil
        \item 12 \ounces paneer, cut into 1-inch cubes
        \item 1 (16-\ounce package) frozen chopped spinach
        \item 1 medium white onion, finely chopped
        \item 1 (1-inch thumb) ginger, peeled and minced (about 1 \tablespoon)
        \item 4 cloves garlic, minced
        \item 1 large green serrano chile, finely chopped (seeds removed if you don't like it spicy!)
        \item \half \teaspoon store-bought or homemade garam masala, recipe follows
        \item 2 \teaspoons ground coriander
        \item 1 \teaspoon ground cumin
        \item \half \cup plain yogurt, stirred until smooth
    }
}{
    \Directions{
        \item In a large bowl, whisk together the turmeric, cayenne, 1 \teaspoon salt and 3 \tablespoons oil.
            Gently, drop in the cubes of paneer and gently toss, taking care not to break the cubes if you're using the homemade kind.
            Let the cubes marinate while you get the rest of your ingredients together and prepped.
        \item Thaw the spinach in the microwave in a microwave-safe dish, 5 minutes on high, then puree in a food processor until smooth.
            Alternatively, you can chop it up very finely with your knife.
        \item Place a large nonstick skillet over medium heat, and add the paneer as the pan warms.
            In a couple of minutes give the pan a toss; each piece of paneer should be browned on one side.
            Fry another minute or so, and then remove the paneer from the pan onto a plate.
        \item Add the remaining 1 \half \tablespoons oil to the pan.
            Add the onions, ginger, garlic and chile.
            Now here's the important part: saute the mixture until it's evenly toffee-coloured, which should take about 15 minutes.
            Don't skip this step - this is the foundation of the dish!
            If you feel like the mixture is drying out and burning, add a couple of \tablespoons of water.
        \item Add the garam masala, coriander and cumin.
            If you haven't already, sprinkle a little water to keep the spices from burning.
            Cook, stirring often, until the raw scent of the spices cook out, and it all smells a bit more melodious, 3 to 5 minutes.
        \item Add the spinach and stir well, incorporating the spiced onion mixture into the spinach.
            Add a little salt and \half \cup of water, stir, and cook about 5 minutes with the lid off.
        \item Turn the heat off.
            Add the yogurt, a little at a time to keep it from curdling.
            Once the yogurt is well mixed into the spinach, add the paneer.
            Turn the heat back on, cover and cook until everything is warmed through, about 5 minutes. Serve.
    }
}
