\Recipe{placeholder}{
    Whole Roasted Red Snapper
}{
    \href{http://www.aveceric.com/all-recipes/whole-roasted-red-snapper-with-thai-spices-and-coconut-rice}{AvecEric}
}{
    \Ingredients{
        \item 4-pound whole red snapper, head on, scales removed and cleaned
        \item \third \cup canola oil
        \item 1 clove garlic, sliced
        \item 1 \tablespoon grated ginger
        \item 1 \tablespoon ground coriander seeds
        \item \half \teaspoon chili flakes
        \item 3 \tablespoons coconut milk
        \item juice and zest of 1 lime
        \item \fourth \cup basil chiffonnade
        \item \fourth \cup cilantro chiffonnade
        \item fine sea salt and freshly ground black pepper 1 lime
    }
}{
    \Directions{
        \item Preheat oven to 400°F.
        \item Generously season inside the belly and both sides of the fish with salt and pepper.
            Place the fish on a roasting pan.
        \item Combine the canola oil with the garlic, ginger, coriander, chili flakes, coconut milk, lime juice and zest in a mixing bowl and stir to combine.
        \item Spoon the spice mixture over the snapper and bake for about 25-30 minutes, basting frequently.
            Bake the fish until a metal skewer can easily be inserted into the fish and, when left in for 5 seconds, feels warm.
        \item While the fish is roasting, cook the rice.
            First, place the rice in a fine sieve and rinse under cool water until the water begins to run clear.
            Transfer rice to a medium pot; add water, season with a pinch of salt, add lemongrass and bring to a boil over medium-high heat.
            Lower the heat and simmer for 10 minutes. Remove the rice from heat, cover and let sit for another 10 minutes.
            When the rice is cooked, remove and discard lemongrass.
            Add the coconut milk and cilantro, gently stir to incorporate and season to taste with lime juice, salt and pepper.
        \item To serve, spoon the coconut rice on to the middle of four plates.
            Fillet the snapper, running a knife lengthwise down the fish at about the center, to separate the side into two fillets, and then under the flesh to separate it from the bone.
            Carefully lift off each fillet and place on top of the rice.
            When the top fillets have been removed, lift off the fish bones and portion the bottom in the same manner.
            Plate the remaining fillets and spoon some of the sauce from the roasting pan over each portion.
            Finish each dish with a squeeze of fresh lime juice and garnish with chiffonade of basil and cilantro.
    }
}
