\recipe{Chicken Tikka Masala}{
        \Ingredients{
            \item 2 tablespoons Ghee or butter
            \item 2 tablespoons ghee (clarified butter)
            \item 1 onion, finely chopped
            \item 4 cloves garlic, minced
            \item 1 tablespoon ground cumin
            \item 1 teaspoon salt
            \item 1 teaspoon ground ginger
            \item 1 teaspoon cayenne pepper
            \item 1/2 teaspoon ground cinnamon
            \item 1/4 teaspoon ground turmeric
            \item 1 (14 ounce) can tomato sauce
            \item 1 cup heavy whipping cream
            \item 2 teaspoons paprika
            \item 1 tablespoon white sugar
            \item 1 tablespoon vegetable oil
            \item 4 skinless, boneless chicken breast halves, cut into bite-size pieces
            \item 1/2 teaspoon curry powder
            \item 1/2 teaspoon salt, or to taste
            \item 1 teaspoon white sugar, or to taste
        }
    }{
        \Directions{
            \item Heat ghee in a large skillet over medium heat and cook and stir onion until translucent, about 5 minutes.
                Stir in garlic; cook and stir just until fragrant, about 1 minute.
                Stir cumin, 1 teaspoon salt, ginger, cayenne pepper, cinnamon, and turmeric into the onion mixture;
                fry until fragrant, about 2 minutes.
            \item Stir tomato sauce into the onion and spice mixture, bring to a boil, and reduce heat to low.
                Simmer sauce for 10 minutes, then mix in cream, paprika, and 1 tablespoon sugar.
                Bring sauce back to a simmer and cook, stirring often, until sauce is thickened, 10 to 15 minutes.
            \item Heat vegetable oil in a separate skillet over medium heat.
                Stir chicken into the hot oil, sprinkle with curry powder, and sear chicken until lightly browned but still pink inside, about 3 minutes; stir often.
                Transfer chicken and any pan juices into the sauce.
                Simmer chicken in sauce until no longer pink, about 30 minutes; adjust salt and sugar to taste.
        }
    }
