\recipe{Jambalaya}{
        \Ingredients{
            \item 2 tablespoons vegetable oil
            \item 1/2 pound andouille or other smoked sausage, cut into 1/2-inch slices
            \item 1/2 cup sliced celery
            \item 1 small onion, chopped
            \item 1 small red or green bell pepper, chopped
            \item 1 clove garlic, minced
            \item 1 3/4 cups chicken broth
            \item 1 cup diced fresh or canned tomatoes
            \item 1 bay leaf
            \item 1 teaspoon TABASCO® brand Original Red Sauce
            \item 1/4 teaspoon dried oregano leaves
            \item 1/4 teaspoon dried thyme leaves
            \item 1/8 teaspoon ground allspice
            \item 3/4 cup uncooked rice
            \item 1/2 pound shrimp, peeled, deveined and cut in half lengthwise
        }
    }{
        \Directions{
            \item Heat oil in a large heavy saucepan or Dutch oven over medium-high heat.
                Add sausage, celery, onion, bell pepper, and garlic.
                Cook 5 minutes or until vegetables are tender, stirring frequently.
            \item Stir in broth, tomatoes, bay leaf, TABASCO Sauce, oregano, thyme, and allspice.
                Bring to a boil, reduce heat, and simmer uncovered for 10 minutes, stirring occasionally.
            \item Stir in rice; cover and simmer 15 minutes.
            \item Add shrimp; cover and simmer 5 minutes longer or until rice is tender and shrimp turn pink.
            \item Let stand, covered, 10 minutes.
                Remove bay leaf before serving.
        }
    }
